Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2018-12-09 article_springer/article_springer.Rmd
Beautify remark

**Remark:**

: If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant.

>>>>

\vspace{12pt}

**Remark.** If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
Equation (2.2) by @Gut1999. @Anderson1987 derives a similar result with a 
different choice of scaling constant.
